---
title: "Weight of Fish"
author: "Amir Johnson / summer 2024"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```


```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.



## Perch

```{r}
fullup <- lm(Weight~ .,data=Perch)
summary.lm(fullup)
```

### Best Models

The data for the adjusted square has a best model for length 1.We can determine this summary has a P-Value of 2.2e-16

### Best Two regressor model

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```
 
  Using the above chart, we can see that the best two regrssor models are height and weight. This model us the best for the perch dara, as well as the elemt model.

## Pike

```{r}
fullup <- lm(Weight~ .,data=Pike)
summary.lm(fullup)
```

### Best Models

The charts best model is the L1-L2-L3, height and Width measurements. This has an estimated p-value of 8.679e-10.

### Best Two regressor model

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topleft",main="Adjusted R^2")
```

The best two element model on the given chart is L1-L3, with and adjusted R squared number of 0.0965
### Best Models


### Best Two regressor model

## Roach

```{r}
fullup <- lm(Weight~ .,data=Roach)
summary.lm(fullup)
```
```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomleft",main="Adjusted R^2")
```

### Best Models

This chart provides that the best overall model is L3 and width

### Best Two regressor model

The best two regressor model is also L3 and width. The Adjusted R squared is 0.821.

## Final Summary Statements